Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-07-17 2016-Weak-FH-Bisim/WeakBisim.tex
petites corrections+figure

\item Finally, for the open transition $\symb{OT}$ in the form ($\set{\beta_{2}}=\beta_{2j}^{j\in J_2}$): $P[Q]_{j_0}	\models \openrule
         {
           \beta_{2j}^{j\in J_2},\Pred_2,\Post_2 }
         {\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha'} \ostate{(t'_l)^{l\in L_Q}}}$\\
If $Q$ moves then we  obtain by Lemma \ref{lem-decompose}:\\
$
		P\models{\openrule
			{
				(\beta_{2j})^{j\in (J_2\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred'_2},  
				{\Post'_2}}
			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha'}
				\ostate{t_l'^{\,l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~}
	Q\models{\openrule
			{
				(\beta_{2j})^{j\in J_2\cap\Holes(Q)}, {\Pred''_2},  
				{\Post''_2}}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha_2}
				\ostate{t_l'^{\,l\in L_Q}}}
		}%\]
$\\
such that  $\Pred_2 \iff {\Pred'_2}
		\land {\Pred''_2}\land \alpha_2=\beta_{2j_0}$, $\Post_2={\Post'_2}\uplus 
		{\Post''_2}$ where ${\Post''_2}$ is the restriction of $\Post_2$ over variables of $\Leaves(Q)$.

@@

Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha_p$ some of them may be non-observable (are $\tau$ transition). By considering $\tau$  actions we split the sequence of actions into $n+1$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many $\tau$ ones.  We can decompose each of the $n+1$ subsequences; for $k\in [0..n]$ the position of the $k^{\text{th}}$ visible action is  $n_k$, for $k\in [1..n]$,  $n'_k$ is any index between $n_{k-1}$ and $n_k$, additionally $n'_0=0$ and $n'_{n+1}=n_1+n_2+3$. We obtain $n+1$ subsequences  made of the following OTs, for all $k\in [0..n]$ :\\
$\forall p\! \in\! [n'_{k}..(n_k\!-\!1)] Q\models{\openrule
			{
				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred''_{p}}},  
				{{\Post''_{p}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
,$ 
$Q\models{\openrule
			{
				\beta_{n_k j}^{j\in J\cap\Holes(Q)}, {{\Pred''_{n_k}}},  
				{{\Post''_{n_k}}}}
				{\ostate{v_{n_kl}^{l\in L_Q}} \OTarrow {\alpha_{{n_k}}}
				\ostate{v_{(n_k+1)l}^{l\in L_Q}}}
				}%\]
$
and
$\forall p \in [(n_k\!+\!1)..(n'_{k+1}\!-\!1)]\,\, Q\models{\openrule
			{
				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred''_{p}}},  
				{{\Post''_{p}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
Thereafter, by Lemma \ref{lem-rel-OT-WOT} we can deduce the following weak open transition:
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma_{kj})^{j\in J\cap\Holes(Q)},  {{\Pred_k}},  
				{{\Post_k}}}
			{\ostate{v_{kl}^{l\in L_Q}} \OTWeakarrow {\alpha'_{k}}
				\ostate{(v_{kl}')^{l\in L_Q}}}
		}%\]
\end{mathpar}
$\alpha_k'=\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post''_{j}}}$\\
$\forall l \in L_Q. v_{kl}=v_{(n'_{k})l} \wedge v_{kl}'=v_{(n'_k)l}$\\
$\displaystyle{\gamma_{kj}^{j\in J\cap\Holes(Q)} }=\displaystyle{\mybigdotcup_{i=n'_{k}}^{(n_k\!-\!1)} \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=i-1}^{n'_{k}}\!\!\!\Post''_{l}}}\dotcup \vis{{\beta_{n_k j}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post''_{l}}}} \dotcup\\
~~\qquad \mybigdotcup_{i=n_k+1}^{n'_{k+1}-1}
\vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}} \subst{\bigotimes_{l=i-1}^{n_k\!+\!1}\!\Post''_{l}\shortotimes\Post''_{n_k}\shortotimes\!\!\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post''_{l}} }\\
%
\Pred_k=\bigwedge_{i=n'_{k}}^{n_k\!-\!1}\!\!\Pred''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\Post''_{j}}\land\Pred''_{n_k} \subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post''_{j}}\land\\ 
~\qquad\quad\bigwedge_{i=n_k+1}^{n'_{k+1}-1}\!\!\!\Pred''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\!\Post''_{j}\shortotimes\Post''_{n_k}\shortotimes\!\!\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\!\Post''_{j}}
\\
\Post_k= \bigotimes_{j=n'_{k+1}-1}^{n'_{k}}\!\!\Post''_{j}$\\

Note that for all $k\in[0..n-1]$, $v_{kl}'=v_{(k+1)l}$, and $v_{0l}=s_{0l}=s_l$ and $v'_{nl}=v_{(n_1+n_2+3) l}=u_{(n_2+1) l} = s'_l$.

By definition of $\Post_k$, we have $\displaystyle{\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post''_{j} = \bigotimes_{j=k-1}^{0}\!\!\Post_{j}}$

%In this case, the number of weak open transitions
%might not be exactly the number of open transitions that take part in the reduction but something smaller, thus the resulting set of weak open transitions could also be smaller.\\
Consequently \[\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{0}\!\!\Post''_{j}}} =
\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post''_{j}\otimes\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post''_{j}}} = \alpha_k'\displaystyle{\subst{\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post''_{j}}} = 
\alpha_k'\displaystyle{\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}}\]
We now have (the $\alpha'_p$ correspond to the observable $\alpha_k$ actions): \TODO{add ref to eq 1 page above?}
\begin{eqnarray*}
\Pred_\beta &\iff& \gamma_{j_0}=
\mybigdotcup_{p=0}^{p=n_1+n_2+2}
\vis{\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}}\\
%&\iff&\gamma_{j_0}=
%\mybigdotcup_{p=0}^{p=n_1+n_2+2}
%\vis{\alpha_{p}\subst{\bigotimes_{j=p-1}^{n'_p}\!\!\Post_{j}}\subst{\bigotimes_{j=n'_p-1}^{0}\!\!\Post_{j}}}\\
%\vis{[\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n_1+n_2+2]]}\\
%&\iff& \gamma_{j_0}=
%\vis{[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[1..n]]}\\
&\iff& \gamma_{j_0}=
[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n]]
\end{eqnarray*}

@@

&\iff\bigwedge_{i=0}^{m_1}\left(\Pred'_{1p}
		\land {\Pred''_{1p}}\land \alpha_{1p}=\beta_{1pj_0}\right)\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}} \\

@@

&\qquad\land\bigwedge_{i=0}^{m_2} \left(\Pred'_{3p}
		\land {\Pred''_{3p}}\land \alpha_{3p}=\beta_{3pj_0}\right) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
&\iff\bigwedge_{i=0}^{m_1}\left((\Pred'_{1p}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}})
		\land ({\Pred''_{1p}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post''_{1j}})\land (\alpha_{1p}=\beta_{1pj_0})\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\right) \\

@@

&\qquad\land\bigwedge_{i=0}^{m_2} \Bigg(\Pred'_{3p} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} 
		\land {\Pred''_{3p}} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}  \\
		 & \qquad \land (\alpha_{3p}=\beta_{3pj_0}) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\Bigg)  \\
&\iff \Pred'\land\bigwedge_{k=0}^n\Pred_k\bigotimes_{j=k-1}^{0}\!\!\Post_{j}\land\Pred_\beta
\\&\iff \Pred'\land\bigwedge_{k=0}^n\Pred_k\bigotimes_{j=k-1}^{0}\!\!\Post_{j}\land
(\gamma_{j_0}=[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n]])

>>>>

\item Finally, for the open transition in the form ($\set{\beta_{2}}=\beta_{2j}^{j\in J_2}$): $P[Q]_{j_0}	\models \openrule
         {
           \beta_{2j}^{j\in J_2},\Pred_2,\Post_2 }
         {\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha'} \ostate{(t'_l)^{l\in L_Q}}}$\\
If $Q$ moves then we  obtain by Lemma \ref{lem-decompose}:\\
$
		P\models{\openrule
			{
				(\beta_{2j})^{j\in (J_2\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred'_2},  
				{\Post'_2}}
			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha'}
				\ostate{t_l'^{\,l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~}
	Q\models{\openrule
			{
				(\beta_{2j})^{j\in J_2\cap\Holes(Q)}, {\Pred''_2},  
				{\Post''_2}}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha_2}
				\ostate{t_l'^{\,l\in L_Q}}}
		}%\]
$\\
such that  $\Pred_2 \iff {\Pred'_2}
		\land {\Pred''_2}\land \alpha_2=\beta_{2j_0}$, $\Post_2={\Post'_2}\uplus 
		{\Post''_2}$ where ${\Post''_2}$ is the restriction of $\Post_2$ over variables of $\Leaves(Q)$.

@@

Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha_p$ some of them may be non-observable (are $\tau$ transition). By considering $\tau$  actions we split the sequence of actions into $n+1$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many $\tau$ ones.  We can decompose each of the $n+1$ subsequences;

\includegraphics[width=6cm]{XFIG/proof-explain}

for $k\in [0..n]$ the position of the $k^{\text{th}}$ visible action is  $n_k$, for $k\in [1..n]$,  $n'_k$ is any index between $n_{k-1}$ and $n_k$, additionally $n'_0=0$ and $n'_{n+1}=n_1+n_2+3$. We obtain $n+1$ subsequences  made of the following OTs, for all $k\in [0..n]$ :\\
$\forall p\! \in\! [n'_{k}..(n_k\!-\!1)] Q\models{\openrule
			{
				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred''_{p}}},  
				{{\Post''_{p}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
,$ 
$Q\models{\openrule
			{
				\beta_{n_k j}^{j\in J\cap\Holes(Q)}, {{\Pred''_{n_k}}},  
				{{\Post''_{n_k}}}}
				{\ostate{v_{n_kl}^{l\in L_Q}} \OTarrow {\alpha_{{n_k}}}
				\ostate{v_{(n_k+1)l}^{l\in L_Q}}}
				}%\]
$
and
$\forall p \in [(n_k\!+\!1)..(n'_{k+1}\!-\!1)]\,\, Q\models{\openrule
			{
				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred''_{p}}},  
				{{\Post''_{p}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
Thereafter, by Lemma \ref{lem-rel-OT-WOT} we can deduce the following weak open transition:
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma_{kj})^{j\in J\cap\Holes(Q)},  {{\Pred_k}},  
				{{\Post_k}}}
			{\ostate{v_{kl}^{l\in L_Q}} \OTWeakarrow {\alpha'_{k}}
				\ostate{(v_{kl}')^{l\in L_Q}}}
		}%\]
\end{mathpar}
$\alpha_k'=\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post''_{j}}}$\\
$\forall l \in L_Q. v_{kl}=v_{(n'_{k})l} \wedge v_{kl}'=v_{(n'_k)l}$\\
$\displaystyle{\gamma_{kj}^{j\in J\cap\Holes(Q)} }=\displaystyle{\mybigdotcup_{i=n'_{k}}^{(n_k\!-\!1)} \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=i-1}^{n'_{k}}\!\!\!\Post''_{l}}}\dotcup \vis{{\beta_{n_k j}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post''_{l}}}} \dotcup\\
~~\qquad \qquad\qquad\mybigdotcup_{i=n_k+1}^{n'_{k+1}-1}
\vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}} \subst{\bigotimes_{l=i-1}^{n_k\!+\!1}\!\Post''_{l}\shortotimes\Post''_{n_k}\shortotimes\!\!\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post''_{l}} }\\
%
\Pred_k=\bigwedge_{i=n'_{k}}^{n_k\!-\!1}\!\!\Pred''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\Post''_{j}}\land\Pred''_{n_k} \subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post''_{j}}\land\\ 
~\qquad\quad\bigwedge_{i=n_k+1}^{n'_{k+1}-1}\!\!\!\Pred''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\!\Post''_{j}\shortotimes\Post''_{n_k}\shortotimes\!\!\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\!\Post''_{j}}
\\
\Post_k= \bigotimes_{j=n'_{k+1}-1}^{n'_{k}}\!\!\Post''_{j}$\\

Note that for all $k\in[0..n-1]$, $v_{kl}'=v_{(k+1)l}$,  $v_{0l}=s_{0l}=s_l$, and $v'_{nl}=v_{(n_1+n_2+3) l}=u_{(n_2+1) l} = s'_l$.

By definition of $\Post_k$, we have $\displaystyle{\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post''_{j} = \bigotimes_{j=k-1}^{0}\!\!\Post_{j}}$.
%In this case, the number of weak open transitions
%might not be exactly the number of open transitions that take part in the reduction but something smaller, thus the resulting set of weak open transitions could also be smaller.\\
Consequently,  we have:
\[\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{0}\!\!\Post''_{j}}} =
\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post''_{j}\otimes\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post''_{j}}} = \alpha_k'\displaystyle{\subst{\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post''_{j}}} = 
\alpha_k'\displaystyle{\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}}\]
We now have (the $\alpha'_p$ correspond to the observable $\alpha_k$ actions): \TODO{add ref to eq 1 page above?}
\begin{eqnarray*}
\Pred_\beta &\iff& \gamma_{j_0}=
\mybigdotcup_{p=0}^{p=n_1+n_2+2}
\vis{\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}}\\
%&\iff&\gamma_{j_0}=
%\mybigdotcup_{p=0}^{p=n_1+n_2+2}
%\vis{\alpha_{p}\subst{\bigotimes_{j=p-1}^{n'_p}\!\!\Post_{j}}\subst{\bigotimes_{j=n'_p-1}^{0}\!\!\Post_{j}}}\\
%\vis{[\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n_1+n_2+2]]}\\
%&\iff& \gamma_{j_0}=
%\vis{[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[1..n]]}\\
&\iff& \gamma_{j_0}=
[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n]]
\end{eqnarray*}

@@

&\iff\bigwedge_{i=0}^{m_1}\left(\Pred'_{1i}
		\land {\Pred''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}\right)\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}} \\

@@

&\qquad\land\bigwedge_{i=0}^{m_2} \left(\Pred'_{3i}
		\land {\Pred''_{3i}}\land \alpha_{3i}=\beta_{3ij_0}\right) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
&\iff\bigwedge_{i=0}^{m_1}\left((\Pred'_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}})
		\land ({\Pred''_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post''_{1j}})\land (\alpha_{1i}=\beta_{1ij_0})\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\right) \\

@@

&\qquad\land\bigwedge_{i=0}^{m_2} \Bigg(\Pred'_{3i} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} 
		\land {\Pred''_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}  \\
		 & \qquad \land (\alpha_{3i}=\beta_{3ij_0}) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\Bigg)  \\
&\iff \Pred'\land\bigwedge_{k=0}^n\Pred_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}\land\Pred_\beta
\\&\iff \Pred'\land\bigwedge_{k=0}^n\Pred_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}\land
(\gamma_{j_0}=[\alpha'_{i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{j}}|i\in[0..n]])
